\documentclass{article}
\usepackage{hyperref}
\title{acm.mst.edu Design Documentation}
\author{Kevin Schoonover}
\date{\today}

\begin{document}

\maketitle

\tableofcontents

\section{Introduction}
\subsection{Purpose}
In order to start on a large-scale project like the ACM-General website, I
believe that it is important to first talk about why we are doing the project.

The main reason that that I started this processes originally was threefold.
Firstly, originally the majority of the System Administrator job was updating
the old ACM-General website by manually uploading photos by inputing them into
wordpress and then creating wordpress events; I personally believed that we
could do better. Secondly, I wanted to create a more succinct and refined user
experience for everyone who interacted with the website thereby increasing user
productivity and activity with ACM. Lastly, I believed that the website was 
capable of so much more than a 'attractive' flier and event share such a
automatically managing SIGs, allowing for developer interaction through an API,
and much more. All of this and more will be discussed throughout this Design
documentation.
\subsection{Tools / Prerequiste Knowledge}
Some tools, frameworks, and languages one should attempt to familiarize 
themselves with to jump head-first into the project:
\begin{itemize}
    \item Django (\url{https://docs.djangoproject.com/en/1.11/}) - Web 
          Framework and backend which runs all of the webpage interaction.
    \item Django REST Framework (\url{http://www.django-rest-framework.org/}) -
          A nice library which helps to automatically configure and manage the
          API.
    \item Git (\url{http://www.sphinx-doc.org/en/stable/}) - Source control
          management software which allows for intelligent sharing and
          management of code.
    \item Jenkins (\url{https://jenkins.io/}) - Another continuous
          integration platform which automatically deploys the website.
    \item Python3 (\url{https://docs.python.org/3/}) - The main programing
          language used in essentially everything we write.
    \item Sphinx (\url{http://www.sphinx-doc.org/en/stable/}) - Automatic
          documentation suite which is a python standard.
    \item Stripe (\url{https://stripe.com/}) - Payment gateway in which all of
          the payments will run through.
    \item Travis CI (\url{https://travis-ci.org/}) - Continuous integration
          platform which runs the automated testing of the code base.
\end{itemize}

\section{Design}
\subsection{Web API}
\subsection{Events}
\subsection{Payments}
\subsection{SIGs}
\subsection{Uesrs}
\subsection{Sponsors}
\subsection{External Developers}
\subsection{Permissions}
\subsection{Testing}
\subsection{Permissions}

\section{Workflow}

\section{Milestones / Deadlines}

\end{document}
